Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2018-08-08 paper/manuscript.tex

\author[1*]{John D. Chodera}
\author[2*]{Antonia S. J. S. Mey}
\author[2*]{Julien Michel}
\author[3*]{David L. Mobley}
\author[4*]{Conor Parks}
\author[5*]{Julia E. Rice}
\author[6*]{Michael Shirts}
\author[7]{Bryce K. Allen}
\author[1]{Levi N. Naden}
\author[1,9]{Andrea Rizzi}
\affil[1]{Computational and Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York NY, USA}
\affil[2]{Departments of Pharmaceutical Sciences and Chemistry, University of California, Irvine, USA}
\affil[3]{EaStCHEM School of Chemistry, David Brewster Road, Joseph Black Building, The King's Buildings, Edinburgh, EH9 3FJ, UK}
\affil[4]{I don't know my affiliation}
\affil[5]{I don't know my affiliation}
\affil[6]{University of Colorado Boulder, Boulder, CO, USA}
\affil[7]{Silicon Therapeutics, Boston, MA, USA}
\affil[8]{Tri-Institutional Training Program in Computational Biology and Medicine, New York, NY, USA}

@@

\subsubsection{Absolute free energy calculations must handle the standard state and use restraints}
\label{sec:standardstate-restraints}

@@

\todo[inline, color={red!40}]{LNN: write common principles alchemical path choice}
\todo[inline, color={red!40}]{AR: write absolute-specific section on  alchemical path choice}
\todo[inline, color={red!40}]{BA: write relative-specific section on  alchemical path choice}

>>>>

\author[1*]{John D. Chodera}
\author[2*]{Antonia S. J. S. Mey}
\author[2*]{Julien Michel}
\author[3*]{David L. Mobley}
\author[4*]{Conor Parks}
\author[5*]{Julia E. Rice}
\author[6*]{Michael Shirts}
\author[7]{Bryce K. Allen}
\author[1]{Levi N. Naden}
\author[1,9]{Andrea Rizzi}
\affil[1]{Computational and Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York NY, USA}
\affil[2]{EaStCHEM School of Chemistry, David Brewster Road, Joseph Black Building, The King's Buildings, Edinburgh, EH9 3FJ, UK}
\affil[3]{Departments of Pharmaceutical Sciences and Chemistry, University of California, Irvine, USA}
\affil[4]{I don't know my affiliation}
\affil[5]{I don't know my affiliation}
\affil[6]{University of Colorado Boulder, Boulder, CO, USA}
\affil[7]{Silicon Therapeutics, Boston, MA, USA}
\affil[8]{Tri-Institutional Training Program in Computational Biology and Medicine, New York, NY, USA}

@@

\subsubsection{Absolute free energy calculations must handle the standard state and use restraints}

\label{sec:standardstate-restraints}

@@
